### 2014-07-09 tex/main-body-text.tex
Edit figure caption slightly.

\begin{figure*}
\begin{center}
	 % NOTE. Eric made Flock-Fig1.jpg as a Preview because Flock-Fig1.pdf
	 % ate up too many resources while editing the document.  For final 
	 % production, it should be changed back to Flock-Fig1.pdf
    \includegraphics[width=\textwidth]{images/Figures-Pat/Flock-Fig1-GreyScale.pdf} % Flock-Fig1.jpg}  
    \caption{Plots of $q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock} made in the program Distruct. Each horizontal plot represents an individual run of the program {\sc structure}, or the 'best run' from a series of runs in {\sc flock}. Within each plot 
$q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock}  are represented by a 
colored vertical bar.  Results from 
from the 'best runs' of {\sc flock} showed similar geographic differentiation to 
\citet{Garzaetal_norcal}.}
    \label{fig:qplots}
\end{center}
\end{figure*}

>>>>

\begin{figure*}
\begin{center}
	 % NOTE. Eric made Flock-Fig1.jpg as a Preview because Flock-Fig1.pdf
	 % ate up too many resources while editing the document.  For final 
	 % production, it should be changed back to Flock-Fig1.pdf
    \includegraphics[width=\textwidth]{images/Figures-Pat/Flock-Fig1-GreyScale.pdf} % Flock-Fig1.jpg}  
    \caption{Plots of $q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock} made with the program {\sc distruct}. Each horizontal plot represents an individual run of the program {\sc structure}, or the ``best run'' from a series of runs in {\sc flock}. Within each plot 
$q_i$ values from {\sc structure} and the normalized likelihood values 
from {\sc flock}  are represented by a 
gray-scale vertical bar. The numbers in parentheses on the right indicate how many {\sc structure} runs (out of 6, as indicated) reached the same solution, or how many groups of {\sc flock} runs (out of 6) had the same ``best run.''}
    \label{fig:qplots}
\end{center}
\end{figure*}
